---
title: "ishratc_AssignPOP"
author: "Ishrat Chowdhury"
date: "November 11, 2019"
output: html_document
---

#Introduction to module

Welcome to the AssignPOP module! By the end of this module you will be able to assign populations to your genetic, non-genetic, or integrated data. 

First we will introduce the package AssignPOP to you. Then we will walk you through some manual examples of population assignment using resampling and cross validation methods Monte Carlo and K-fold cross validations. We will go over how to check the accuracy of the population asisgnments.

Then we will show you have to do all that and much more in with AssignPOP.

#Intro to package

AssignPOP is an


#General pipeline

First lets load the packages.
```{r}
library(assignPOP)
library(curl)
```

Now lets load our genomic data. This genomic data is in the GENEPOP format, but you can also import from te STRUCTURE format using the complementary function.
```{r}
f1 <- curl("https://github.com/cavega36/AssignPopModule/blob/master/simGenepop.txt")
simGenepop.txt <- read.table(f1, header = TRUE, sep="\t", stringsAsFactors = FALSE)
head(simGenepop.txt)
```

It will look really funky now. We have to use an AssignPOP function to make it usable. Note that the following code might take a few minutes to run.

```{r}
YourGenepop <- read.Genepop( "simGenepop.txt", pop.names=c("pop_A","pop_B","pop_C"), haploid = FALSE)
```

That looks good! We now have genetic data loaded.

We can also remove low variance loci with the following code (optional).

```{r}
YourGenepopRd <- reduce.allele( YourGenepop, p = 0.95)
```

Now lets do the same for the non-genetic data

```{r}
f2 <- curl("https://github.com/cavega36/AssignPopModule/blob/master/morphData.csv")
morphData.csv <- read.csv(f2, header = TRUE, sep = ",", stringsAsFactors = FALSE)
#Import morphometric data containing sample IDs and features
morphdf <- read.csv( "morphData.csv", header=TRUE )
#Create a string vector for population label (repeat each name for 30 individuals)
pop_label <- c( rep("pop_A", 30), rep("pop_B", 30), rep("pop_C", 30) ) 
#Add the pop_label to the last column; 'morphdf_pop' is a data frame with population label in the last column
morphdf_pop <- cbind(morphdf, pop_label)

#Handling numeric population name
#A set of population names: 1, 2, and 3
pop_label <- c( rep(1, 30), rep(2, 30), rep(3, 30))
#Add the pop_label
morphdf_pop <- cbind(morphdf, pop_label)
#Convert population name to factor data type 
morphdf_pop$pop_label <- as.factor(morphdf_pop$pop_label)
head(morphdf_pop)
```

Now our non-genetic data is loaded!

The neat thing about AssignPOP is that you can even combine genetic and non-genetic data. The non-geentic data just needs to be in a .csv format with the first column correspodning to the ID's of the genetic data. This may take soem time to run!

```{r}
YourIntegrateData <- compile.data( YourGenepopRd, "morphData.csv")
```

Now we have integrated data!

Let's start some analysis.

#Examples without the package

#Examples with the package 

#References 





